% Cover letter using letter.cls
\documentclass[14]{letter}
\usepackage[T1]{fontenc}
\usepackage{url}
\makeatletter
\def\url@linkstyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\ttfamily}}}
\makeatother
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Ryan Neufeld}                % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left
 
\begin{letter}{ \\
Berkman Center\\
Harvard University \\} 

\LARGE
\textbf{\textsc{Ryan Neufeld}}\\
\large
\begin{center}
\vspace{-.7in}
\line(1,0){474}\\

\begin{tabular}{@{}l @{\hspace{81 mm}}r}
259 Pembina Drive & 1.204.823.1839\\
Morden, MB & rkneufeld@gmail.com\\
R6M 1H7
\end{tabular}
\end{center} \vfill % forces letterhead to top of page
\normalsize

\opening{Re: GSoC 2009: Berkman Center} 
 
\noindent I am sending this email to indicate that I will be applying for a position with the Berkman Center as part of Google Summer of Code 2009. It is my intention to contribute to the Cohort CRM project mentoring under Daniel Collis-Puro, whom I have been in dialog with over the past week.

\noindent Last summer, during GSoC 2008, I contributed to the Thousand Parsec project, and got a taste for what it was to finally commit to something real -- something tangible. After my return to school that fall I began learning Ruby and Ruby on Rails at the behest of two colleagues of mine. In a few months time they saw I had come very far, and decided they would start mentoring me. 

\noindent Since then I have spent a great deal of time learning various tools and techniques, and made a point of integrating RoR into my education at every opportunity. Two of the projects I have worked on have been a formal software engineering project and an industrial project building a Real Estate search engine. Through these projects I developed knowledge of web application development; Test-Driven development; Agile methodologies; Javascript and jQuery; how to use deployment tools and much more. And now GSoC 2009 approaches...

\noindent It is my hope that the Cohort project can offer me some real, tangible experience with RoR and web application development; Do for me what GSoC 2008 did for me as a developer in general. I thank you for your time and consideration.

\closing{Sincerely,}
%checked
  
%\encl{Resume}					% Enclosures

\end{letter}
 

\end{document}













