% File:     eqdw.tex
% Tim Herd <timherd@eqdw.net>
% Modified: <2015.02.07>

\documentclass[margin,line,letterpaper]{resume}

\begin{document}
\name{\Large Tim Herd}
\begin{resume}


  %______________________________________________________________________________________
  % Contact Information
  \section{\mysidestyle Contact\\Information}\vspace{2mm}

  \begin{tabular}{@{} l @{\hspace{100mm}} r}
  Oakland, CA           & timherd@eqdw.net \\
                         & github: eqdw     \\
                         & skype: rzeqdw

  \end{tabular}


  %______________________________________________________________________________________
  % Technical Expertise
  \section{\mysidestyle Technical\\Expertise}

  {\bf Programming\\ }
    \begin{tabular}{@{{{\scriptsize}}} l @{\hspace{28mm}}l }
    Languages  & Ruby, Java/CoffeeScript, Clojure, Erlang/Elixir, Java  \\
    Frameworks & Ruby on Rails, jQuery, Ember.js\\
    \end{tabular}

  {\bf Tools\\}
    \begin{tabular}{@{{{\scriptsize}}} l @{\hspace{10mm}}l}
      IDEs & Vim, Emacs, Eclipse \\
      Web Servers & Nginx, Apache, Mongrel \\
      Databases & Postgres, Mysql, SQLite \\
      Messaging & RabbitMQ, Kafka \\
      Source Control Systems & Git \\
   \end{tabular}


  %______________________________________________________________________________________
  % Education
  \section{\mysidestyle Education}

  {\bf B.Sc.~Computer Science}, University of Manitoba \hfill {\bf Oct 2010}


 %______________________________________________________________________________________
  % Awards and Accomplishments
  \section{\mysidestyle Awards and\\Accomplishments}

  \begin{list2}
    \item Dean's Honour List recipient, 2008, 2009
    \item Top 10\%, IEEEXtreme 24-hour programming competition, 2009
  \end{list2}


  %______________________________________________________________________________________
  % Service
  \section{\mysidestyle Service}

  \begin{list2}
    \item TA, Clojurebridge San Francisco, 2014
    \item Organizer, Railsbridge San Francisco, 2013 - 2015
    \item Teacher, Railsbridge San Francisco, 2012 -- 2015
    \item Member, Skullspace (Winnipeg Hackerspace), 2010 -- 2012
    \item Treasurer, U of M Computer Science Students' Association, 2009 -- 2010
    \item Member, U of M IEEE Student Branch \& Computer Society, 2007 -- 2011
    \item Charter Member, Winnipeg Ruby Users Group, 2010 -- Present
    \item Member, U of M Unmanned Aerial Vehicle group, 2008 -- 2009
 \end{list2}



  %______________________________________________________________________________________
  % Employment
  \section{\mysidestyle Work}

  \employer{\bf Funding Circle}
  \title{\bf Senior Software Engineer}
  \dates{September 2015 -- Present}
  \location{}
  \begin{position}
    Full stack Ruby and Clojure engineer. Built and maintained
    cluster of micro-services written in Ruby and Clojure, relating
    to collecting credit and business data from inbound borrowers.
    Formally mentored junior engineers. Acted as liaison between
    software development and information security, and engaged in
    security outreach and education to the non-technical side of
    the office. Solo engineer on several small internal projects.
  \end{position}

  \employer{\bf Blurb}
  \title{\bf Software Engineer}
  \dates{August 2013 -- September 2015}
  \location{}
  \begin{position}
    Full stack Ruby on Rails developer. Worked on the web team
    maintaining existing legacy systems and building out new
    functionality around the e-commerce platform and related
    workflows. Maintained APIs and wrote front-end ember.js code
    for complex client-side behaviours
  \end{position}

  \employer{\bf Coupa Software}
  \title{\bf Software Engineer}
  \dates{May 2012 -- July 2013}
  \location{}
  \begin{position}
    Full stack Ruby on Rails developer. Worked with development and
    product design teams to fix bugs and implement customer-facing
    features.
  \end{position}

  \employer{\bf Innovatis, Inc.}
  \title{\bf Junior Solutions Developer}
  \dates{January 2011 -- December 2011}
  \location{}
  \begin{position}
    Worked on various contract projects. Built websites from scratch
    in HTML/CSS/Javascript. Developer on several Ruby on Rails
    projects. Lead developer on one Rails project.
  \end{position}

  \employer{\bf Complex Games}
  \title{\bf Junior Application/Web Developer}
  \dates{July 2010 -- January 2011}
  \location{}
  \begin{position}
    Rebuilt website in Joomla CMS. Created custom Joomla theme.
    Built promotional sites for special occasions.
    Contributed to in-house game development code
  \end{position}

\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF
