% File:     ryan_neufeld.tex
% Ryan Neufeld <rkneufeld@gmail.com>
% Modified: <2009-03-17 20:49:45 CDT>

\documentclass[margin,line,letterpaper]{resume}

\begin{document}
\name{\Large Ryan K. Neufeld}
\begin{resume}

  %______________________________________________________________________________________
  % Contact Information
  \section{\mysidestyle Contact\\Information}\vspace{2mm}

  \begin{tabular}{@{} l @{\hspace{76mm}} r}
  259 Pembina Drive      & 1.204.823.1839         \\
  Morden, MB~ R6M 1H7    & rkneufeld@gmail.com     \\

  \end{tabular}

  %______________________________________________________________________________________
  % Technical Expertise
  \section{\mysidestyle Technical\\Expertise}

  Proficient with Windows, Mac, and Linux environments. \\
  Proficient with Ruby on Rails environment, including various test, deployment and other gems \& tools. \\
  Fluent in Ruby, Javascript, C/C++, Java, and X/HTML. \\
  Conversant in Clojure, CLisp,  Python, CSS and others.\\
  Practioner of both Pragmatic and Agile Programming.

  %______________________________________________________________________________________
  % Education
  \section{\mysidestyle Education}

  {\bf B.Sc. Computer Science} \vspace{2mm}\\\vspace{1mm}%
  {\sl University of Manitoba} \hfill {\bf 2005 -- 2010}

  %______________________________________________________________________________________
  % Employment
  \section{\mysidestyle Work}

  {\bf Chromium 53 Consulting}, Winnipeg, MB \vspace{2mm}\\\vspace{1mm}%
  {\sl Consultant} \hfill {\bf August 2008 -- Present}\\
  Joined a budding business specializing in software development, design, and
  consulting for the World Wide Web. Currently mentoring under two founders learning Ruby \& Ruby on Rails technologies. Current projects include a Real Estate fuzzy-search engine \& developing a base template for new projects.

{\bf Thousand Parsec Project}, USA \& Australia (Telecommuted) \vspace{2mm}\\\vspace{1mm}%
  {\sl Student Developer } \hfill {\bf April 2008 -- August 2008}\\
  Spent summer working with my mentoring organization, the Thousand Parsec Project, as part of the Google Summer of Code program. Completed in a full small-scale project cycle, developing a new ruleset for the self-named game framework. Development took place exclusively in C++, building a version of the board game Risk. The project was finished far ahead of schedule and I continued on to create an SVG map importer and a short series of screencasts.

  {\bf Pembina Valley Computers}, Morden, MB \vspace{2mm}\\\vspace{1mm}%
  {\sl PC Repair Technician} \hfill {\bf August 2007 -- December 2007}\\
  Worked with a small local outfit providing both retail PC sales and technical support. Acted in both an administrative and a technical capacity, maintaining stock levels, building new consumer systems and providing both hardware and software based technical support.

  {\bf Sasktel}, Regina, SK \vspace{2mm}\\\vspace{1mm}%
  {\sl Tier 2 Technical Assistant -- Co-op} \hfill {\bf January 2007 -- August 2007}\\
  Worked with Tier 2 technical assistants to provide technical support to internal customers. This work focused on systems installations, software tutorials and general troubleshooting. The Sasktel environment consisted of Windows XP Machines running Office 2003, with Clarify CRM as a ticketing system.

  %______________________________________________________________________________________
  % Service
  \section{\mysidestyle Personal Traits}

  \begin{list2}
    \item Fiercly dedicated and devoted
    \item Outgoing and enjoyable to work with
    \item Self-motivated
    \item Strong leadership and customer satisfaction skills
  \end{list2}

  %______________________________________________________________________________________
  % Service
  \section{\mysidestyle Service}

  \begin{list2}
    \item President, U of M Computer Science Students' Association, 2008 -- Present
    \item Member, U of M IEEE Student Branch \& Computer Society, 2008 -- Present
    \item Volunteer, Pembina Valley Humane Society, 2008 -- Present
  \end{list2}

  \newpage
  %______________________________________________________________________________________
  % Projects
  \section{\mysidestyle Projects}

  \begin{list2}
    \item Twitter-sms (http://github.com/neufelry/twitter-sms)
    \item Real estate recommendation engine (private project)
    \item Report card generation application for primary education (preliminary)
    \item Many other small projects (http://github.com/neufelry)
  \end{list2}


  %______________________________________________________________________________________
  % Awards and Accomplishments
  \section{\mysidestyle Awards and\\Accomplishments}

  \begin{list2}
    \item Dean's Honour List recipient, 2009.
    \item 3rd in Manitoba, ACM International Collegiate Programming Contest Regionals, 2008.
    \item Academic Excellence throughout high school (2002 -- 2005).
    \item Director of one-act play at Winston Knoll Collegiate, 2005
    \item Elected Winston Knoll Student Council Mayor, (2004 -- 2005)
    \item Attended prestigious Interchange on Canadian Studies, 2004.
    \item Travelled to England \& Ireland with Highschool group, 2004
  \end{list2}

  %______________________________________________________________________________________
  % References
  \section{\mysidestyle References}

  {\sl Available on request.}

%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

